Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-10 analysis/paper/sim_survey_paper.Rmd
Work table up to survey settings

The next step in the simulation is to distribute the abundance-at-age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations was generated with a resolution of $r$ and a depth gradient. The depth gradient was set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation, and the age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations was controlled by a smoothing ($\lambda$) and scaling parameter ($\kappa$) [@Blangiardo2015] and correlation across ages and years was controlled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process was controlled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in Appendix 1.

@@

$$n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A}{r^2} q_a )$$
Where $n_{a,y,s}$ is the number of fish sampled by a set, $A$ indicates the area covered by the trawl, $r$ is the resolution of the grid cells, and $q_a$ is the catchability coefficient of each age. Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. The lengths of the fish sampled by the set are then simulated using the original von Bertalanffy growth curve [@Cailliet2006]:

@@

**Parameter name**   **Symbol**   **Setting**
------------------   ----------   -----------
              Ages          $a$          1:20
             Years          $y$          1:20
  Mean recruitment      $\mu_r$           30M

>>>>

The next step in the simulation is to distribute the abundance-at-age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations was generated with a resolution of $R$ and a depth gradient. The depth gradient was set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The simulated population is distributed through the grid by simulating spatial-temporal noise controlled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation, and the age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations was controlled by a smoothing ($\lambda$) and scaling parameter ($\kappa$) [here we approximate $\kappa$ from a range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years was controlled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process was controlled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in Appendix 1.

@@

$$n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$$
Where $n_{a,y,s}$ is the number of fish sampled by a set, $A_{trawl}$ indicates the area covered by the trawl, $A_{cell}$ is the area of a grid cell (i.e. $R^2$), and $q_a$ is the catchability coefficient of each age. Here, catchabilities were defined using a logistic curve controlled by a steepness, $k$, and midpoint parameter, $x_0$. The lengths of the fish sampled by the set are then simulated using the original von Bertalanffy growth curve [@Cailliet2006]:

@@

                                       **Parameter name**                   **Symbol**      **Setting**
---------------------------------------------------------   --------------------------   --------------
                                              *Abundance*
                                                     Ages                          $a$             1:20
                                                    Years                          $y$             1:20
                                         Mean recruitment                      $\mu_r$              30M
                    Standard deviation of log-recruitment                   $\sigma_r$              0.5
                                     Mean total mortality                      $\mu_Z$              0.7
                    Standard deviation of total mortality                   $\sigma_Z$              0.2
  Correlation across ages in error around total mortality      $\varphi_{\delta, age}$              0.9
 Correlation across years in error around total mortality     $\varphi_{\delta, year}$              0.5
                                                   *Grid*
                                               Grid cells                          $s$           1:6400
                                               Resolution                          $r$           3.5 km
                                              Shelf depth                  $d_{shelf}$            200 m
                                              Shelf width                  $w_{shelf}$           100 km
                                              Depth range         $[d_{min}, d_{max}]$    [0 m, 1000 m]
                                      Number of divisions                    $N_{div}$                1
                                         Number of strata                  $N_{strat}$               42
                                           *Distribution*
        Standard deviation of age-year-space distribution               $\sigma_{\xi}$              2.8
                        Smoothness of spatial correlation                    $\lambda$                1
                             Range of spatial correlation                          $r$            50 km
          Correlation across ages in spatial distribution         $\varphi_{\xi, age}$             0.1*
         Correlation across years in spatial distribution        $\varphi_{\xi, year}$              0.9
            Depth at which abundance is typically highest                      $\mu_d$            200 m
                Dispersion around depth of peak abundance                   $\sigma_d$             70 m

\* Distribution set to be equal for ages 5+
